Runtime Feedback in a Meta-Tracing JIT for Efficient Dynamic Languages

### 2011-04-13 talk/icooolps2011/paper.tex
change x = hint(x, promote=True) to just promote(x) to reduce confusion

\cfbolz{XXX more precise definition of what promote does}
\cfbolz{change the hint(x, promote=True) syntax to something more readable}

@@

Observe how the first two operations could be constant-folded if the value of
$x_1$ were known. Let's assume that the value of \texttt{x} in the Python code can vary, but does so
rarely, i.e. only takes a few different values at runtime. If this is the
case, we can add a hint to promote \texttt{x}, like this:
\begin{lstlisting}[mathescape,basicstyle=\ttfamily]
def f1(x, y):
    x = hint(x, promote=True)
    z = x * 2 + 1
    return z + y
\end{lstlisting}

The hint indicates that \texttt{x} is likely a runtime constant and the JIT
should try to perform runtime specialization on it
in the code that follows. When just running the code, the function has no
effect, as it simply returns its first argument. When tracing, some extra work
is done. Let's assume that this changed function is traced with
the arguments \texttt{4} and \texttt{8}. The trace will be the same, except for one
operation at the beginning:

@@

    def f(self, val):
        self = hint(self, promote=True)
        self.y = self.compute() + val

>>>>

\cfbolz{XXX more precise definition of what promote does}

@@

Observe how the first two operations could be constant-folded if the value of
$x_1$ were known. Let's assume that the value of \texttt{x} in the Python code can vary, but does so
rarely, i.e. only takes a few different values at runtime. If this is the
case, we can add a hint to promote \texttt{x}, like this:
\begin{lstlisting}[mathescape,basicstyle=\ttfamily]
def f1(x, y):
    promote(x)
    z = x * 2 + 1
    return z + y
\end{lstlisting}

The hint indicates that \texttt{x} is likely a runtime constant and the JIT
should try to perform runtime specialization on it
in the code that follows.\footnote{For technical reasons the promote hint needs
to be written down slightly differently in the actual code.}  When just running
the code, the \texttt{promote} function has no
effect. When tracing, some extra work
is done. Let's assume that this changed function is traced with
the arguments \texttt{4} and \texttt{8}. The trace will be the same, except for one
operation at the beginning:

@@

    def f(self, val):
        promote(self)
        self.y = self.compute() + val
